\documentclass[10pt,a4paper]{article}


%\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
%\usepackage{lmodern}
\usepackage[sfdefault,light]{roboto}
%sfdefault,light,condensed,thin


\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{kotex}
\usepackage{fontawesome5}

\include{structure} 
%\hyphenation{Some-long-word} 
\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------
\newcommand{\name}{Eloy Alvarado Narváez}
\newcommand{\address}{Valparaíso, Chile.}
\newcommand{\phone}{+56 9 85682232}
\newcommand{\email}{ealvaradonarvaez@gmail.com}
\newcommand{\github}{ealvnrz}
\newcommand{\linkedin}{ealvnrz}

\begin{center}
\huge\name\\
\normalsize PhD candidate and university lecturer \\
\address\\
\faIcon{mobile-alt} \phone \hspace{5pt}|\hspace{5pt} \faIcon[regular]{envelope} \href{mailto:\email}{\email}
\hspace{5pt}|\hspace{5pt} \faIcon{github} \href{https://github.com/ealvnrz}{\github}
\hspace{5pt}|\hspace{5pt} \faIcon{linkedin} \href{https://www.linkedin.com/in/ealvnrz/}{\linkedin}
\end{center}

%\spacedhrule{0.9em}{-0.4em} 

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

%\roottitle{Summary} 
%\vspace{-0.3em} 
%\noindent Statistician+
%\spacedhrule{0.5em}{-0.4em} 
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------



\roottitle{\faIcon{graduation-cap} Education \hrulefill } 


\headedsection 
{\href{https://ideuv.uv.cl/index.php/es/?view=page&id=91}{Universidad de Valparaíso}}
{\textsc{Valparaíso, Chile}}
 {
\headedsubsection 
{\textsc{PhD in Statistics}}
{2017 -- Present}
{\bodytext{PhD. candidate under the supervision of Prof. Moreno Bevilacqua. \\Thesis title: ``Clayton copula random fields with application to spatial data with bounded support''.}}
}

%------------------------------------------------
\headedsection 
{\href{http://www.korea.ac.kr}{Korea University / 고려대학교 }}
{\textsc{Seoul, South Korea}}
 {
\headedsubsection 
{\textsc{Exchange program}}
{2014 -- 2014}
{\bodytext{Relevant courses included: Introduction to Data Mining \& Advanced reading and discussion in English.}}
}


\headedsection 
{\href{http://www.pucv.cl}{Pontificia Universidad Católica de Valparaíso}}
{\textsc{Valpara\'iso, Chile}} {

\headedsubsection 
{Bachelor in Statistics / Statistician }
{2013 -- 2015}
{\bodytext{Lecturer assistant for introductory and advanced courses (3-4 each semester)\\
Thesis title: ``\textit{Ecuaciones diferenciales estocásticas con aplicación en matemática financiera: Modelo de Black-Scholes}'' (Stochastic differential equations with applications in mathematical finance: The Black-Scholes model).\ Graduation grade: 6.1 (1-7 scale).}
\textbf{DREAMS program}: To
Develop Research of Excellence for Advanced Meritorious Students \ 
\bodytext{Research assistant under supervision of Prof. Natalia Bahamonde: ARCH models with weighted liquidity.}}
}

%------------------------------------------------

\headedsection
{\href{http://www.usm.cl}{Universidad Técnica Federico Santa María}}
{\textsc{Valparaíso, Chile}} {

\headedsubsection 
{Mathematical civil engineering, \textnormal{Applied statistics major (discontinued).}}
{2009 -- 2012} {}
}

%%\spacedhrule{0.5em}{-0.4em} 

%----------------------------------------------------------------------------------------
%	TEACHING SECTION
%----------------------------------------------------------------------------------------

\roottitle{\faUniversity\ Academic Experience \hrulefill}

\headedsection 
{\href{https://ideuv.uv.cl/}{Instituto de Estadística, Universidad de Valparaíso }}
{\textsc{Valparaíso, Chile}} {
\headedsubsection 
{University lecturer}
{August '19 -- Present}
{\bodytext{Lecturer of several courses for undergraduate programs:\\
 Data science and statistical engineering, Construction engineering \& Bachelor in Physics.
  \\ \textbf{Course list}:
  \begin{itemize}
  \item IEST 213: Statistical Methods %[2019]
  \item IEST 322 \& IEST 422: Sampling theory I and II, respectively %[2019,2020,2021]
  \item IEC 311: Probability and statistics %[2020,2021]
  \item LFIS 325: Statistics for physical sciences %[2020,2021]
  \item IECD 325: Linear models and experimental designs. %[2021]
  \end{itemize}
}}}

\headedsection 
{\href{http://www.estadistica.cl}{Instituto de Estadística, Pontificia Universidad Católica de Valparaíso}}
{\textsc{Valparaíso, Chile}} {
\headedsubsection % Job title entry for the current employer
{University teaching workshops}
{January '18 -- February '18}
{\bodytext{Organized by  \href{http://innovaciondocente.ucv.cl/}{\textit{Unidad de Mejoramiento de la Docencia Universitaria (UMDU)}}:
\begin{itemize}
\item \textit{``Aprendizaje Activo: Diseñando mi clase''} (Active Learning: designing my class)
\item \textit{``Evaluar y Retroalimentar con apoyo de las TIC''} (Evaluate and provide feedback with support of ICT).
\end{itemize}
}}
\headedsubsection 
{University Lecturer}
{March '17 -- December '17}
{\bodytext{Lecturer of introductory statistics courses for the undergraduate programs of electrical and electronic engineering.
}}}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{\faIcon{briefcase} Work Experience \hrulefill}
%------------------------------------------------
\headedsection 
{\href{http://www.ifop.cl}{Instituto de Fomento Pesquero}}
{\textsc{Remote / Valparaíso, Chile}} {

\headedsubsection 
{External Adviser}
{July '21 -- Present}
{\bodytext{Spatio-temporal modeling advisor for the project \textit{``Marine Mammal Bycatch Risk Assessment in Chile''}, funded by San Francisco State University.
}}}


%------------------------------------------------
\headedsection 
{\href{http://www.equifax.com}{Equifax Inc.}}
{\textsc{Santiago, Chile / Atlanta, USA}} {

\headedsubsection 
{Statistical Analyst}
{April '16 -- February '17}
{\bodytext{Statistical Analyst for the Data \& Analytics group. In charge of acting as a bridge between statistical analyst in Alpharetta, USA and the software development center in Chile. Among the activities carried out include: validation of attribute creation models, database validation, optimization and support of SAS code, SAS administrator, statistical support within a distributed environment.
}}}

%------------------------------------------------
\headedsection 
{\href{http://www.banchileinversiones.cl}{Banchile Inversiones}}
{\textsc{Santiago, Chile}} {

\headedsubsection 
{Intership}
{January '15 -- February '15}
{\bodytext{Internship in the Business Intelligence division, working in the creation of a predictive
model to capture new customers of an specific investment product. My work was the
complete creation of the model using information from the BI databases and the presentation of the results to management.}}}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{\faIcon{cog} Skills \hrulefill} 

\inlineheadsection
{Programming Languages}{R, Python, C++, \LaTeX, SQL, SAS.}
\inlineheadsection
{Softwares:}{Tableau, SPSS, STATA, MS suite.}

%------------------------------------------------

\inlineheadsection 
{Languages:}
{Español/Spanish \textit{(native language)}, English \textit{(Full professional proficiency, TOEFL iBT score: 90, November, 2015)}, Korean/한국어 \textit{(Beginner A2, Korea University)}, French/Français \textit{(Beginner A1, Institut Français).}}

%------------------------------------------------


%----------------------------------------------------------------------------------------
%	RESEARCH AND SCIENTIFIC EVENTS
%----------------------------------------------------------------------------------------

\roottitle{\faIcon[regular]{file-alt}  Research \hrulefill}
%fix with .bib once published
\inlineheadsection 
{Accepted or published research article:}{}

\begin{enumerate}
\item Víctor Beltrán, Pablo Acuña-Mardones, Jaime Díaz, \textbf{Eloy Alvarado} and Alfredo von Marttens. \textit{``TEGO: A new concept of teledentistry for the elderly through a web platform and mobile app in the context of the COVID-19 pandemic''}, Journal of Oral Research. \textit{Accepted article, scheduled for publication in Supplementary Issue 2, 2021}.
\item Cristina Sanzana-Luengo, Leonardo Díaz, Liliann Abarza, \textbf{Eloy Alvarado} and Víctor Beltrán. \textit{``Teledentistry protocol for the elderly in the context of the COVID-19 pandemic through a web platform / mobile app: approach from the general dentist''}. Journal of Oral Research. \textit{Accepted article, scheduled for publication in Supplementary Issue 2, 2021}.
\end{enumerate}
\inlineheadsection 
{Manuscripts under review:}{}
\begin{enumerate}
\item M. Stehlik, J. Kiselak, A. Dinamarca, \textbf{Eloy Alvarado}, F. Plaza, F. Medina Marín, S. Stehlikova, B. Venegas, A. Gajdos, Y. Li, S. Katuscak, A. Brazinova A, Y. Lu. \textit{``REDACS: Regional emergency driven adaptive cluster sampling for effective COVID-19 prevalence''}. Stochastic Analysis and Applications, \textit{under final review}.
\end{enumerate}

\inlineheadsection 
{Working papers:}{}
\begin{enumerate}
\item Moreno Bevilacqua, \textbf{Eloy Alvarado}, Christian Caamaño, Fernando Quintana. \textit{``Clayton copula random fields with application to spatial data with bounded support''}. \textit{finishing the manuscript}.
\item Marco Flores, \textbf{Eloy Alvarado} , Christina Sanzana-Luengo. \textit{``Experience of caries and tooth loss in the chilean elderly population benefited by TEGO project in the context of Covid-19 pandemic.''}. \textit{finishing the manuscript}.
\end{enumerate}

\roottitle{\faFileInvoiceDollar \ Grants and projects \hrulefill}
\begin{itemize}
\item National Doctoral Degree Scholarship, ANID, 2018. N° 2018-21180953
\item \textit{``Semi-presential technological support platform for urgent and
priority dental care for the elderly in the context of the COVID-19 pandemic in the Chilean population''}, funded by the Rapid Allocation of Funds of the National Agency of Research and
Development (ANID), Reference No. COVID0766, Chile. \textbf{Collaborator}.
\end{itemize}




\roottitle{\faComments[regular] Scientific Events \hrulefill}
\begin{itemize}
\item Attendant, XIX Valparaíso Statistical Week, Valparaíso, Chile, 2013. \\ Organizer:  \href{http://www.upla.cl}{Universidad de Playa Ancha}
\item Presenter, ``\textit{Stochastics differential equations in mathematical finance: The Black-Scholes Model}'', XXI Valparaíso Statistical Week, Valparaíso, Chile, 2015. \\ Organizer: \href{http://www.pucv.cl}{Pontificia Universidad Católica de Valparaíso}
\item Attendant, XLII National Convention on Statistics, Concepción, Chile, 2015. \\
Organizer:  \href{http://www.soche.cl}{ Chilean Statistical
Society}
\end{itemize}

\end{document}